{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-30 Paper/main.tex
Small notation thing for training and holdout set
Notation consistency changes

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega_0) = f(t)$ of $F(\omega)$.

	\begin{equation}
		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t)
	\end{equation}

@@

	\begin{equation}
		f(t) = \sum_{k =0}^{K} c_k(t -w)^{k}
	\end{equation}
	can be expressed as a finite linear combination of the monomials $(t - w)^{k}$ with coefficient $c_k$ which form the basis

	\begin{equation}
		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
	\end{equation}
	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase. This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		S_{i}^{FB}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			S_{l,0}^{BS}(x) = &
			\begin{cases}
				1 & \text{if} \quad x \in \left[\tau_l, \tau_{l+1}\right)\\
				0 & \text{otherwise}
			\end{cases}\\ \\
			S_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} S_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} S_{l+1,m-1}^{BS}(x)
		\end{split}
	\end{equation}

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	{\color{red} Write something about how to approximate functions by truncating the basis.}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$. On the one hand, this way is not efficient since the technique with too many basis functions can even approximate a noise of the sample curves which possibly interrupts the analysis. On the other hand, the important information on the curves would be missed with a too-small number of basis functions. This discussion challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, maintain significant fluctuation. The basis expansion with truncation is by:
	\begin{equation}
		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t) = \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j(\omega_0) b_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error. The number $L$ is subjectively chosen but we can fix the nubmer through a more reasonable method, Cross-Validation, which minimizes Mean Squared Error (MSE).

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$. Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

	This decomposition can be used to express the random vector $X(\omega)$ in the following way.

	\begin{equation}
		X(\omega) = \mu_x + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_x + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
	\end{equation}

@@

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

	\begin{equation}\label{MeanFunction}
		\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]
	\end{equation}

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	{\color{orange}suggestion from here}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

@@

	Therefore, we can approximate the function $F$ with first few eigenfunctions. The functions $F$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g. $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$). Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. {\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}

	\begin{equation}\label{KarhunenLoeve}
		F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
	\end{equation}

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(F(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector. {\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}

@@

	In the typical scalar setting, a similar consideration leads to the concept of principal components. This is also possible in a functional setting. Let $\{f_1(t), \dots, f_n(t)\}$ be a set of i.i.d. realizations generated by a random function $F(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogues for the mean and covariance functions.

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)
	\end{equation}

@@

	\begin{equation}
		f_i(t) = \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}

@@

	\begin{equation}
		Y(\omega) = \alpha + \Psi\left(F(\omega)\right) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)F(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

	Where $f(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible. Therefore, other options have to be considered.

@@

	\begin{equation}
		\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} c_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} c_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} c_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
			= \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
			= \alpha + \sum_{j = 1}^{J} c_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( f_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} ({\color{red} X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)} ) {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
		\end{split}
	\end{equation}

>>>>

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $X(\omega_0) = x(t)$ of $X(\omega)$.

	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_{j}(\omega_0) \phi_j(t)
	\end{equation}

@@

	\begin{equation}
		x(t) = \sum_{i \in \mathcal{I}} c_i(t -w)^{i}
	\end{equation}
	can be expressed as a finite linear combination of the monomials $(t - w)^{i}$ with coefficient $c_i$ which form the basis

	\begin{equation}
		\phi_{i}^{M}(t) = (t-w)^k \quad i \in \mathcal{I}
	\end{equation}
	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase. This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			\phi_{l,0}^{BS}(x) = &
			\begin{cases}
				1 & \text{if} \quad x \in \left[\tau_l, \tau_{l+1}\right)\\
				0 & \text{otherwise}
			\end{cases}\\ \\
			\phi_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} \phi_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} \phi_{l+1,m-1}^{BS}(x)
		\end{split}
	\end{equation}

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	{\color{red} Write something about how to approximate functions by truncating the basis.}
	As above-mentioned, the realized curves can be estimated with basis functions. For the basis expansion, it is technically possible to use all basis functions $b_{j \in \mathcal{I}}$. On the one hand, this way is not efficient since the technique with too many basis functions can even approximate a noise of the sample curves which possibly interrupts the analysis. On the other hand, the important information on the curves would be missed with a too-small number of basis functions. This discussion challenges the researcher to seek a point at which they truncate the basis function in order to remove noise and, at the same time, maintain significant fluctuation. The basis expansion with truncation is by:
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error. The number $L$ is subjectively chosen but we can fix the nubmer through a more reasonable method, Cross-Validation, which minimizes Mean Squared Error (MSE).

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$. Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

	This decomposition can be used to express the random vector $V(\omega)$ in the following way.

	\begin{equation}
		V(\omega) = \mu_V + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_V + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
	\end{equation}

@@

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $X$ are defined as follows.

	\begin{equation}\label{MeanFunction}
		\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]
	\end{equation}

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	{\color{orange}suggestion from here}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through c : $[0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

@@

	Therefore, we can approximate the function $X$ with first few eigenfunctions. The functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order (e.g. $Var(\xi_{j}) \geq Var(\xi_{k})$ for all $j > k$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. {\color{orange} The proofs are provided at \ref{Proof1} and \ref{Proof2}.}

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
	\end{equation}

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi_j(\omega) = \langle X(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector. {\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}

@@

	In the typical scalar setting, a similar consideration leads to the concept of principal components. This is also possible in a functional setting. Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogues for the mean and covariance functions.

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)
	\end{equation}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}

@@

	\begin{equation}
		Y(\omega) = \alpha + \Psi\left(X(\omega)\right) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

	Where $x(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible. Therefore, other options have to be considered.

@@

	\begin{equation}
		\beta(t) = \sum_{j = 1}^{\infty} b_j \phi_j(t)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} b_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
			= \alpha + \sum_{j \in \mathcal{I}} \left[ b_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[b_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
			= \alpha + \sum_{j = 1}^{J} b_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
		\end{split}
	\end{equation}

@@

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( f_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^{m, \mathcal{T}} \psi_{k}(s)\right)} \mathrm{d}s \\
			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}^{\mathcal{H}}\sum_{k \in \mathcal{L}}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
		\end{split}
	\end{equation}
